Quantifying the manageability of pollination networks in an invasion context

### 2017-02-28 paper/draft_2.Rmd
Update awknowledgements

The authors thank Dr. Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions. 
EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency. 
DBS acknowledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.

>>>>

The authors thank Dr. Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon Mora, Guadalupe Peralta, Rogini Runghen, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions. 
EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency. 
DBS acknowledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.
